---
title: "Developing Data Products Course Project: Wage prediction model"
author: "Nobumasa Hayashi"
date: "12/10/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Executive Summary

In this project, I build a linear regression model with multiple predictors to fit the wage from a data set of "Mid-Atlantic Wage Data". Here, I chose three predictors including "age", "job class", and "education level". Based on this model, my shiny app predicts the wage from your choices of "age", "job class" and "education level".


## Shiny application and related repository
My shiny app is posted on the following website.
<https://nobumasah5183.shinyapps.io/wage_fit/>

GitHub repository containing related files is the following.
<https://github.com/NobumasaHayashi/DDP_peer_graded_assignment>


## The concept of this model 
The model is constructed by the following code.

```{r preparation, warning=FALSE, echo=TRUE, results=FALSE, message = FALSE}
library(ISLR)
library(plotly)
library(caret)
data(Wage)
inTrain <- createDataPartition(y=Wage$wage,
                               p = 0.7, list = FALSE)
training <- Wage[inTrain,]; testing <- Wage[-inTrain,]
modFit <- train(wage ~ age + jobclass + education,
                method = "lm", data = training)
finMod <- modFit$finalModel
finMod$coefficients
```

## Prediction of the wage using the model
The constructed model predict the outcome pretty well.
```{r prediction, echo=TRUE,warning = FALSE}
pred <- predict(modFit, testing)
plot_ly(x = ~testing$wage, y = ~pred,mode = "markers", type = "scatter")
```

